Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-31 notes/privacy-proof/main.tex
update the privacy proof notes

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
\section{Preliminaries}
\label{sec_background}

@@

\section{Technical Problem Statement and Motivations}
\label{sec_moti}
We are interested in designing a mechanism for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.

However, in previous works, the accuracy of the posterior was measured again with respect to $\ell_1$ norm. That is, an upper bound was given on
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as defined above. This accuracy metric is meaningless when the results released are distributions rather than numerical values. In contrast, distribution metrics such as $f$-divergence, Hellinger distance, etc. come into mind overtly when we are measuring distance between distributions. This gives us motivation on using a different norm (a distribution metric) to compute the sensitivity
and provide guarantees on the accuracy.

Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$:
Given two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ the following equality holds 
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)=
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]

Our choice to use Hellinger distance is motivated by three facts:
\begin{itemize}
\item It simplifies calculations in the case of the probabilistic models considered here.
\item It also automatically yields bounds on the total variation distance, which represents also the maximum advantage
an unbounded adversary can have in distingishing two distributions. 
\item The accuracy can be improved by using a smooth bound on Hellinger distance's local sensitivity. As shown in Fig. \ref{fig_sensitivity}, taking advantage of the gap between the global sensitivity and local sensitivity, we can improve the accuracy by applying a smooth upper bound on local sensitivity instead of using global sensitivity.
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{sensitivity_2d.eps}
\caption{{Sensitivity of $\hellinger$}}
\label{fig_sensitivity}
\end{figure}
\end{itemize}

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\sum_{r'\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\Big)}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

@@

\subsection{Privacy Analysis for Baseline Mechanisms}
In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}. The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.

\subsection{Privacy Analysis for $\hexpmech$}

The differential privacy property of $\hexpmech$ is proved based on following two lemmas: Lemma \ref{lem_sliding} and Lemma \ref{lem_dilation}.\\

\noindent \textbf{Sliding Property of $\hexpmech$}
\begin{lem}
\label{lem_sliding}
Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
\end{equation*}

\end{lem}

\begin{proof}

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
 \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$. In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.

 \begin{thm}
 \label{thm_hellinegr_equality_beta}
 for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
  $$
  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2, \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
  $$
 \end{thm}

\begin{thm}
 \label{thm_hellinegr_equality_dirichlet}
 In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
  $$
  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2),
  $$
  where $set(\cdot)$ means we only consider the value of each dimension in the vector without the order.
 \end{thm}

 \begin{thm}
 \label{thm_candidate_divide}
 There are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either 
 $$
 = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
 $$ or 
 $$
 =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
 $$
 \end{thm}
 \begin{proof} of Theorem \ref{thm_candidate_divide}.

 Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e. $u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.

 From Theorem \ref{thm_hellinegr_equality_beta}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 \end{proof}

\begin{thm}
 \label{thm_candidate_divide_dirichlet}
 In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
 $$
 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
 = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
 $$ 
 and $|z| = \frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$, where $\sum{|a_i|} = \sum{|b_i|} = k$.
 \end{thm}

 \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.

 Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
 $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
 $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
 Then, there are $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible permutation when the condition in Theorem \ref{thm_hellinegr_equality_dirichlet} is satisfied.
 \end{proof}

 In Beta-binomial system, let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$. The proofs are given by parts:

 \begin{itemize}
 	\item for $r \in R_1$:

		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
		\begin{equation*}
		\begin{split}
		LHS 
		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
		\end{split}
		\end{equation*}

		By bounding the $\delta' \geq -S(\dataobs)$, we can get:

		\begin{equation*}
		\begin{split}
		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
\end{itemize}

The same in Dirichlet-multinomial distribution, partitioning the $\candidateset$ by the possible value of $|z|$, the proof can be derived in the same way as above by part.

\end{proof}

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = e^{\lambda} c] + \frac{\delta'}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.

More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$.
\end{lem}

\begin{proof}
Based on Theorem \ref{thm_hellinegr_equality_beta} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.

The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.

We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$. Consider the event $G = \{ \hexpmech(\dataobs) : u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$. Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.\\

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
	\end{equation*}
	for $z \in R_1$.

	Let $Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.

	After simplification, we need to show: $u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

\begin{itemize}
	\item $\lambda < 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
		\end{equation*}
		is always true when $\lambda < 0$
	\item $\lambda > 0$

		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs))$. Then, what we need to proof under the case $\lambda > 0$ is:
		\begin{equation}
		\label{eq_dilation_case2}
		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
		\end{equation}

		Based on the accuracy property of exponential mechanism:
		\begin{equation*}
		\begin{split}
		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
		\end{split}
		\end{equation*}
		we derived the accuracy bound for $\hexpmech$:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs)) \leq c] 
		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
		\end{split}
		\end{equation*}

		In Beta-binomial system, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
		\end{split}
		\end{equation*}

		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.

		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.

\end{itemize}

\end{proof}

\noindent \textbf{$(\epsilon, \delta)-$Differential Privacy of $\hexpmech$}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
\end{lem}

\begin{proof}

>>>>

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle

\section{Preliminaries}
\label{sec_background}

@@

\section{$\gamma$ -Smooth Sensitivity}
\label{sec_mechs}
$S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets, and $\gamma = 1$.

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs')} +\gamma + d(\dataobs,\dataobs')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two datasets, and $\gamma = 0.5$.
\end{definition}

@@

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $2\epsilon$-differential privacy in Beta-binomial system.
\end{lem}

\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.
  By Definition \ref{def_epsilon_delta_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:

  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
  \begin{equation*}
  \hexpmechPr{\dataobs}{z = r} \leq e^{2\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
  \end{equation*}

  By definition \ref{def_smoo}:

  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\nomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\nomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon}{2} \big) \\
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)\\
  \end{split}
  \end{equation*}

  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:

  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$ smooth sensitivity: $|\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)}| \leq \gamma$:

  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2} \cdot \gamma
  \big)\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}
  Doing the same transformation in the denominator:

  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:

  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:

    \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$ smooth sensitivity: $|\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')}| \leq \gamma$ $\implies$
  $\frac{- \epsilon}{2}
  (\frac{1}{S(\dataobs)}-
  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{2} \cdot \gamma$
      \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon}{2} \cdot \gamma
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2} +   \frac{- \epsilon}{2} \cdot \gamma
  \big)
  }\\
  & = e^{(\epsilon + \epsilon \cdot \gamma )} \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset{\dataobs}} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  }\\
  & = e^{( \epsilon + \epsilon \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
  \end{split}
  \end{equation*}

  By setting the $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
\end{proof}
